SBML L3 paper response to reviewers

### 2020-01-11 main.tex
Put marker for latexdiff
Update on Overleaf.

Dear Thomas, and reviewers,

@@

These are important issues indeed.  In the revised manuscript, we have added text in the section titled ``Forthcoming challenges'' to acknowledge and touch upon some of the costs and benefits.  We feel that a more extended discussion of these topics have to be considered beyond the scope of this paper, but we hope that the new changes are enough to address the point to a reasonable extent.

@@

>>>>

Dear Dr.\ Lemberger and anonymous reviewers,

@@

These are important issues indeed.  In the revised manuscript, we have added text in the section titled ``Forthcoming challenges'' to acknowledge and touch upon some of the costs and benefits.  We feel that a more extended discussion of these topics has to be considered beyond the scope of this paper, but we hope that the new changes are enough to address the point to a reasonable extent.

@@

\clearpage
\emph{LATEXDIFF TO BE APPENDED HERE ...}
